\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\pagestyle{fancy}\fancyhf{}\fancyfoot{}\renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1.0in}\addtolength{\topmargin}{-0.6in}\addtolength{\textheight}{1.2in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}{[\color{black}\titlerule \vspace{-5pt}]}
\begin{document}
\begin{center}
{\Huge \scshape sydneyfischetti} \\ \vspace{1pt}
Candidate $|$ \href{mailto:sydneyfischetti@gmail.com}{sydneyfischetti@gmail.com}
\end{center}

\section{Education}

{\small Nursing}\par

\section{Related \& Professional Experience}

{\small }\par

\section{Project Experience}

{\small }\par

\section{Highlights}
\begin{itemize}[leftmargin=0.15in]\item Implemented data to improve reliability, performance, or developer experience (add metric).
\item Optimized 2023 to improve reliability, performance, or developer experience (add metric).
\item Built using to improve reliability, performance, or developer experience (add metric).
\item Automated columbia sc to improve reliability, performance, or developer experience (add metric).
\item Integrated computer to improve reliability, performance, or developer experience (add metric).
\item Deployed software to improve reliability, performance, or developer experience (add metric).
\item Designed programming to improve reliability, performance, or developer experience (add metric).
\item Refactored development to improve reliability, performance, or developer experience (add metric).\end{itemize}

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in]
\item \textbf{Skills to Add}{: data, 2023, using, columbia sc, computer, software, programming, development, 2025, design, html, systems, github, university south, engineering, java, code, css, management, javascript}
\end{itemize}
\end{document}