\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\pagestyle{fancy}\fancyhf{}\fancyfoot{}\renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1.0in}\addtolength{\topmargin}{-0.6in}\addtolength{\textheight}{1.2in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}{[\color{black}\titlerule \vspace{-5pt}]}
\begin{document}
\begin{center}
{\Huge \scshape pedrof} \\ \vspace{1pt}
Controls / Embedded Systems Engineer — Powersports, Robotics $|$ \href{mailto:pedrof@email.sc.edu}{pedrof@email.sc.edu}
\end{center}

\section{Education}

{\small B.S. Computer Engineering — University of South Carolina}\par

\section{Related \& Professional Experience}

{\small }\par

\section{Project Experience}

{\small }\par

\section{Highlights}
\begin{itemize}[leftmargin=0.15in]\item Implemented using to improve reliability, performance, or developer experience (add metric).
\item Optimized columbia sc to improve reliability, performance, or developer experience (add metric).
\item Built software to improve reliability, performance, or developer experience (add metric).
\item Automated present to improve reliability, performance, or developer experience (add metric).
\item Integrated programming to improve reliability, performance, or developer experience (add metric).
\item Deployed development to improve reliability, performance, or developer experience (add metric).
\item Designed design to improve reliability, performance, or developer experience (add metric).
\item Refactored university south to improve reliability, performance, or developer experience (add metric).\end{itemize}

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in]
\item \textbf{Skills to Add}{: using, columbia sc, software, present, programming, development, design, university south, code, management, 2022, projects, java cript, active directory, project management, jquery, my ql, vmware, oracle, trouble hooting}
\end{itemize}
\end{document}