\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\pagestyle{fancy}\fancyhf{}\fancyfoot{}\renewcommand{\headrulewidth}{0pt}\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}\addtolength{\textwidth}{1.0in}\addtolength{\topmargin}{-0.6in}\addtolength{\textheight}{1.2in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}{[\color{black}\titlerule \vspace{-5pt}]}
\begin{document}
\begin{center}
{\Huge \scshape sydneyfischetti} \\ \vspace{1pt}
Nurse/Health Care $|$ \href{mailto:sydneyfischetti@gmail.com}{sydneyfischetti@gmail.com}
\end{center}

\section{Education}

{\small Nursing}\par

\section{Related \& Professional Experience}

{\small }\par

\section{Project Experience}

{\small }\par

\section{Highlights}
\begin{itemize}[leftmargin=0.15in]\item Implemented cu tomer  ervice to improve reliability, performance, or developer experience (add metric).
\item Optimized project management to improve reliability, performance, or developer experience (add metric).
\item Built active directory to improve reliability, performance, or developer experience (add metric).
\item Automated trouble hooting to improve reliability, performance, or developer experience (add metric).
\item Integrated proce  improvement to improve reliability, performance, or developer experience (add metric).
\item Deployed micro oft office to improve reliability, performance, or developer experience (add metric).
\item Designed java cript to improve reliability, performance, or developer experience (add metric).
\item Refactored vendor management to improve reliability, performance, or developer experience (add metric).\end{itemize}

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in]
\item \textbf{Skills to Add}{: cu tomer  ervice, project management, active directory, trouble hooting, proce  improvement, micro oft office, java cript, vendor management, bu ine  analy i, data analy i, ql, ale, cheduling, ecurity, reporting, jquery, data entry, html, technical  upport, cu tomer  upport}
\end{itemize}
\end{document}